INTEGRAL TRANSPORT CORRECTION TO DIFFUSION CALCULATIONS\\ USING THE pCMFD SCHEME

### 2019-11-06 docs/PHYSOR2020/pCMFD-RM-PHYSOR2020.tex
Amend mistaken comment
Daniele: I removed a confusing comment.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper]{physor2020}
%
%  various packages that you may wish to activate for usage
\usepackage{tabls}
\usepackage{cites}
\usepackage{epsf}
\usepackage{appendix}
\usepackage{ragged2e}
\usepackage[top=1in, bottom=1.in, left=1.in, right=1.in]{geometry}
\usepackage{enumitem}
\setlist[itemize]{leftmargin=*}
\usepackage{caption}
\captionsetup{width=1.0\textwidth,font={bf,normalsize},%
              skip=0.3cm,within=none,justification=centering}
\usepackage{bm}
\usepackage{tikz}
\usepackage{xfrac}
\usepackage{units}

@@

\daniele{Although I have used drift-advection many times, somebody may argue that this is not the correct word because advection is often related to a term depending on the first derivative of the unknown. It is not the case here. One can note however that in heat transfer it is possible find convection terms whose derivative is replaced by a finite difference with a bulk quantity. Under that approximation, one recovers our term by a change of variable. So, I let you choose the most appropriate word, and if asked, I'll know my answer anyway.}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper]{physor2020}
%
%  various packages that you may wish to activate for usage
\usepackage{tabls}
\usepackage{cite}
\usepackage{epsf}
\usepackage{appendix}
\usepackage{ragged2e}
\usepackage[top=1in, bottom=1.in, left=1.in, right=1.in]{geometry}
\usepackage{enumitem}
\setlist[itemize]{leftmargin=*}
\usepackage{caption}
\captionsetup{width=1.0\textwidth,font={bf,normalsize},%
              skip=0.3cm,within=none,justification=centering}
\usepackage{bm}
\usepackage{tikz}
\usepackage{xfrac}
\usepackage{units}

@@
